IJAR Bayesian Nonparametrics Special Issue Manuscript

### 2015-10-21 ijar-npb-ms.tex
minor stuff

\author[ein]{Gero Walter}
\ead{g.m.walter@tue.nl}
\author[oxf]{Louis J.M. Ashlett}
\ead{louis.aslett@stats.ox.ac.uk}
\author[dur]{Frank P.A. Coolen}
\ead{frank.coolen@durham.ac.uk}

@@

@@

***Also calculate $\Rsys(t)$ intervals for vacuous prior ($[\yktzl, \yktzu] = [0,1]$ for some fixed $\nktz$)?***

>>>>

\author[ein]{Gero Walter\fnref{fn1}}
\ead{g.m.walter@tue.nl}
\author[oxf]{Louis J.M. Ashlett}
\ead{louis.aslett@stats.ox.ac.uk}
\author[dur]{Frank P.A. Coolen}
\ead{frank.coolen@durham.ac.uk}

@@

\fntext[fn1]{Gero Walter was supported by the Dinalog project
``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'' (CAMPI).}

@@

***Also calculate $\Rsys(t)$ intervals for vacuous prior
($[\yktzl, \yktzu] = [0,1]$ for both fixed $\nktz$ and interval $[\nktzl, \nktzu]$)?***
